\thesisTitle

### 2019-10-08 proposal/paper.tex
started describing the lta uninorms approach

This thesis will be based on two currently mostly unrelated fields of research:
\begin{enumerate*}
	\item Aggregation function learning
	\item Graph classification
\end{enumerate*}.
A short overview of the current state-of-the-art approaches in both fields will be given now.

\subsection{Aggregation Function Learning}%
\label{sec:related-work:lta}

>>>>

This thesis will be based on two currently mostly unrelated fields of research:
\begin{enumerate*}
	\item Learning to Aggregate
	\item Graph classification
\end{enumerate*}.
A short overview of the current state-of-the-art approaches in both fields will be given now.

\subsection{Learning to Aggregate}%
\label{sec:related-work:lta}

Two main approaches to represent the aggregation function in LTA problems have been explored.
The first approach uses so-called uninorms~\cite{Melnikov2016} to do so.
There the basic idea is to express composite valuations as fuzzy logical assignments $y \in [0, 1]$.
Such a composite assignment $y$ is modeled as the result of a parameterized logical expression of constituent assignments $y_i \in [0, 1]$.
As the logical expression that thus effectively aggregates the constituents, a uninorm $U_{\lambda}$ is used.
Depending on the parameter $\lambda$, a uninorm interpolates between t-norms and t-conorms which correspond to logical conjunction and disjunction respectively.
\begin{align*}

\end{align*}
